Mixture distribution data generation

### 2022-02-14 Ch3_samplesize/Datagen_viz.Rmd
Code for simulating individual densities is done

```{r echo=TRUE}
# MIXTURE MODEL --------------------------------------------------
## Mixture proportions ----------------------------------------
# We assume four categories of individuals with increasing movement.

@@

# CASE1

pars <- desired_mean_sd(mean = c(160, 300, 600, 1000), sd = c(90, 120, 160, 200))

# Special case I am considering where for each category the mean doubles, and then sd=mean*0.6
# pars <- desired_mean_sd(mean = c(150, 300, 600, 1200), sd = c(90, 180, 360, 720))

@@

### PLOT the mixture components -------------------------------
lnorm_densities <- purrr::map(1:4, function(y) stat_function(fun = dlnorm,
                                                             args = list(meanlog = mus[y], sdlog = sigsqs[y]),
                              color = dens_cols[y], size=1))
ggplot() +
  lnorm_densities +
  theme_minimal() +
  labs(y = "Density") +
  lims(x = c(0, 150)) -> densities_plot
densities_plot

@@

@@

>>>>

```{r echo=TRUE, fig.width=9, fig.height=4}
# MIXTURE MODEL --------------------------------------------------
## Mixture proportions ----------------------------------------
# We assume four categories of individuals with increasing movement.

@@

# CASE1
means <- c(160, 300, 600, 1000)
sds <- c(90, 120, 160, 200)

# Special case I am considering where for each category the mean doubles, and then sd=mean*0.6
# means <- c(150, 300, 600, 1200)
# sds <- c(90, 180, 360, 720)

pars <- desired_mean_sd(mean = means, sd = sds)

@@

### PLOT the mixture components -------------------------------
lnorm_densities <- purrr::map(1:4, function(y) stat_function(fun = dlnorm,
                                                             args = list(meanlog = mus[y], sdlog = sigsqs[y]),
                              color = dens_cols[y], size=1))
ggplot() +
  lnorm_densities +
  theme_minimal() +
  labs(y = "Density") +
  lims(x = c(0, 150)) +
  #scale_y_sqrt(limits = c(0, NA)) +
  NULL -> densities_plot
densities_plot

@@

Now, let's simulate the individuals

```{r}
pars_df <- data.frame(sgroup = 1:ngroup, npergroup = npergroup, pis = pis, mu = mus, sigsqs = sigsqs, mean = means, sd = sds)
#pars_df

Thinking out loud: Let's make the variation for the individuals normal. So, we multiply the variance for that percentage and then estimate it? The mu stays the same, we do a sample from the standard normal? Or do we follow percentages. Since we have a different number of individuals per group, I'd go with the standard normal approach.

@@

indiv_pars <- data.frame()

for(i in 1:ngroup){
  nindiv <- pars_df$npergroup[i]
  indiv.means <- rep(pars_df$mean[i], nindiv)
  indiv.var <- rnorm(nindiv, sd = 0.3)
  indiv.sds <- pars_df$sd[i] + (pars_df$sd[i]*indiv.var)

  indiv.pars <- desired_mean_sd(mean = indiv.means, sd = indiv.sds)

  sgroup <- pars_df$sgroup[i]
  id <- paste0("G", sgroup, ".I", 1:nindiv)

  a <- cbind(id, sgroup, indiv.means, indiv.var, indiv.sds, indiv.pars)

  indiv_pars <- rbind.data.frame(indiv_pars, a)

}

```{r}
# make the curves for each individual

indiv_densities <- purrr::map(1:nrow(indiv_pars), function(y) stat_function(fun = dlnorm,
                                                             args = list(meanlog = indiv_pars$mu[y], sdlog = indiv_pars$sigsq[y]),
                              color = dens_cols[indiv_pars$sgroup[y]], size=1, alpha = 0.5))
ggplot() +
  indiv_densities +
  lnorm_densities +
  theme_minimal() +
  labs(y = "Density") +
  lims(x = c(0, 150)) +
  #scale_y_sqrt(limits = c(0, NA)) +
  NULL -> indiv_densities
indiv_densities

```{r eval=FALSE}
